Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-08-16 Ben_Manuscripts/Outlines/Paper1_Outline.tex
Update Paper1_Outline.tex

>>>>

Basin A and Basin B are two configurationally metastable basins. 
\begin{itemize}
	\item We hesitate to classify the basins as separate phases
	\item We hypothesize that Basin B is present at higher temperatures
	\item This is evidenced by a simulation of a system in Basin A whose temperature was linearly ramped from 280K to 340K over 100 ns
	\item Visually, there is a distinct change in pore structure
	\item To quantify our observations we chose 3 easily measurable order parameters: the distance between pores, the membrane the thickness and the ratio of pore radius to the uncertainty in pore radius.
	\item The distance between pores was measured as described previously
	\item The membrane thickness was measured using the length of the z-box vector
	\item The pore radius was measured by calculating the distance between the center of mass of each aromatic ring and the center of mass of all aromatic rings in respective pores.
	\item The pore radius is divided by its uncertainty in order to understand the degree to which monomers obstruct the pore region.
	\item We observe changes in slope around 310K indicating the possibility of an abrupt change in system ordering
	\item To prove that the basins are in fact two different phases, we search for a first order phase transition, which would be indicated by a discontinuity in an order parameter.
	\item Our 100 ns temperature ramp may have been to fast to avoid hysteresis
	\item To mitigate hysteresis, we started with structures equilibrated at 280K. The temperature was raised to 300K and allowed to equilibrate for 200 ns.
	\item At the end of 200 ns, the temperature was raised 5K and equilibrated again for 200 ns. This processed continued until we reached 325K. 
	\item We observed only smooth changes in order parameters as temperature was increased indicating that we have not found two phases.
\end{itemize}
